% references section

\begin{thebibliography}{[1]}
%\bibstyle{splncs}

\bibitem{Milner1}
R. Milner,
\emph{A Calculus of Communicating Systems},
Lecture Notes in Computer Science, vol. 92, Springer-Verlag, 1980

\bibitem{Milner2}
R. Milner,
\emph{Communication and Concurrency},
Prentice-Hall, 1989

\bibitem{HandbookProcessAlgebra}
J.A. Bergstra, A. Ponse, S.A. Smolka, 
\emph{Handbook of Process Algebra}, 
Elsevier Science B.V., 2001

\bibitem{Keller}
R.M. Keller,
\emph{Formal Verification of Parallel Programs},
Communications of the ACM, 19(7), pp. 371-384, 1976

\bibitem{ReactiveSystems}
L. Aceto, A. Ingolfsdottir, K. G. Larsen, J. Srba,
\emph{Reactive Systems - Modeling, Specification and Verification},
Cambridge University Press, 2007

\bibitem{Park}
D.M.R. Park,
\emph{Concurrency and Automata on Infinite Sequences},
In: Proceedings of the 5th G.I.Conference in Theoretical Computer Science, 
Lecture Notes in Computer Science, vol. 104, Springer-Verlag, pp. 167-183, 1981

\bibitem{UnderstandingConcurrentSystems}
A.W. Roscoe,
\emph{Understanding Concurrent Systems},
Texts in Computer Science, Springer-Verlag, 2010

\bibitem{Milner3}
R. Milner,
\emph{Operational and Algebraic Semantics of Concurrency Processes},
In: J. van Leeuwen (ed.) Handbook of Theoretical Computer Science, pp. 1201-1242,
Elsevier and MIT Press, 1990

\bibitem{ModelChecking}
C. Baier, J.-P. Katoen, 
\emph{Principles of Model Checking},
The MIT Press, 2008

\bibitem{HennessyMilner}
M.C.B. Hennessy, R. Milner,
\emph{Algebraic Laws for Nondeterminism and Concurrency},
Journal of the ACM, 32(1), pp. 137-161, 1985

\bibitem{Larsen}
K.G. Larsen,
\emph{Proof Systems for satisfiability in Hennessy–Milner logic with recursion}, 
Theoretical Computer Sciece, 72(2-3), Special Issue, pp. 265–288, 1990

\bibitem{Jar}
The Java tutorials,
\emph{Packaging Programs in JAR Files},
\url{http://download.oracle.com/javase/tutorial/deployment/jar/index.html}

\bibitem{Aldebaran}
CADP manual, 
\emph{Aldebaran format for Labeled Transition Systems},
\url{http://www.inrialpes.fr/vasy/cadp/man/aldebaran.html#sect6}

\bibitem{CWB}
\emph{The Edinburgh Concurrency Workbench (CWB)},	
\url{http://homepages.inf.ed.ac.uk/perdita/cwb/summary.html}

\bibitem{mCRL2}
\emph{micro Common Representation Language 2 (mCRL2)},	
\url{http://www.mcrl2.org}

\bibitem{MWB}
\emph{The Mobility Workbench (MWB)},
\url{http://www.it.uu.se/research/group/mobility/mwb}

\bibitem{CADP}
\emph{Construction and Analysis of Distributed Processes (CADP)},
\url{http://www.inrialpes.fr/vasy/cadp.html}

\bibitem{LTSA}
\emph{Labelled Transition System Analyser (LTSA)},
\url{http://www.doc.ic.ac.uk/ltsa/}

\bibitem{Fernandez}
J.-C. Fernandez, 
\emph{An Implementation of an Efficient Algorithm for Bisimulation
Equivalence}, Science of Computer Programming, vol. 13, pages 219-236, 1989/1990

\bibitem{ABP1}
W.C. Lynch, 
\emph{Computer systems: Reliable full-duplex file transmission over half-duplex telephone line},
Communications of the ACM, vol. 11, no. 6, pp. 407–410, 1968

\bibitem{ABP2}
K.A. Bartlett, R.A. Scantlebury, P.T. Wilkinson, 
\emph{A note on Reliable Full-duplex Transmission over Half-duplex Links},
Communications of the ACM, vol. 12, pp. 260–261, 1969

\bibitem{Peterson}
G.L. Peterson,
\emph{Myths about the Mutual Exclusion Problem}, 
Information Processing Letters, 12(3), pages 115-116, 1981

\bibitem{ModellingAndAnalysis}
J.F. Groote, M. Reniers, 
\emph{Modelling and Analysis of Communicating Systems}\emph, 
Technical University of Eindhoven, rev. 1478, 2009

\bibitem{Chomsky}
N. Chomsky,
\emph{Three Models for the Description of Language},
IEEE Transactions on Information Theory, 1956

\bibitem{Compilers}
A.V. Aho, R. Sethi, J.D. Ullman,
\emph{Compilers: Principles, Techniques, and Tools}
Addison Wesley, 2006

\bibitem{ANTLR}
T. Parr, 
\emph{The Definitive ANTLR Reference - Building Domain-Specific Languages}, 
The Pragmatic Bookshelf, 2007

\bibitem{PaigeTarjan}
R. Paige, R. Tarjan, 
\emph{Three Partition Refinement Algorithms}\emph, 
SIAM J. Comput. 16 (6), 1987

\bibitem{PiazzaPolicriti}
A. Dovier, C. Piazza, A. Policriti, 
\emph{An Efficient Algorithm for Computing Bisimulation Equivalence}\emph, 
Theoretical Computer Science 311, pages 221-256, 2004

\bibitem{Kulick}
Seth Kulick,
\emph{Process Algebra, CCS, and Bisimulation Decidability},
University of Pennsylvania, pages 8-10, 1994

\bibitem{ProcessAlgebraParallel}
M.Alexander, W.Gardner,
\emph{Process Algebra for Parallel and Distributed Processing},
Chapman\&Hall/CRC Press, Computational Science Series, pages 114-118, 2009

\bibitem{HMLRecursion}
L. Aceto, A. Ingolfsdottir,
\emph{Testing Henessy-Milner logic with Recursion},
BRICS Report Series, pages 3-5, 1998

\bibitem{Dekker}
E. W. Dijkstra,
\emph{Co-operating Sequential Processes}, 
In F. Genuys, editor, Programming Languages, pages 43112. Academic Press, New York, 1968
Reprinted from: Technical Report EWD-123, Technological University, Eindhoven, the Netherlands, 1965

\end{thebibliography}