\section{Conclusions and Future Work}
In this paper we presented a tool for modeling, manipulation and analysis of concurrent systems. It includes recognizing CCS expressions, building LTS graphs and checking equivalence between two LTS graphs with respect to strong and weak bisimilarity. WThe tool is in initial development phase, however it is already fully functional to perform specification and verification of concurrent systems described as CCS expressions and/or LTS graphs. We have successfully tested the tool with large number of examples comparing the results obtained with mCRL2 and CWB, and we also presented few examples showing the tool usage. 

Future work can include optimization of the tool response times for very large LTS graphs, as well as implementation of prunung strategy for infinite LTS graphs. It would be also usefull if the LTS graph is better visualized where every SOS rule is shown, with its source and sink nodes showing the CCS expression for each of the nodes. Such a visualization can be very helpfull for understanding the semantics of the CCS language for students that are starting to study it. Furthermore, the LTS minimization and LTS comparison functionality which at the moment includes only strong and weak bisimilarity can be extended to include other behavioural equivalences as well. There is an idea to extend the tool to support not only CCS expressions and LTS in aldebaran format, but also other process languages and other file formats as well. In general, our vision for future development of the tool on the long run is directed towards building a tool that will unite all the functionalities and best characteristics of the similar existing tools which are already in use.
