% references section

\begin{thebibliography}{[1]}
%\bibstyle{splncs}

\bibitem{Milner1}
R. Milner,
\emph{A Calculus of Communicating Systems},
Lecture Notes in Computer Science, vol. 92, Springer-Verlag, 1980

\bibitem{Milner2}
R. Milner,
\emph{Communication and Concurrency},
Prentice-Hall, 1989

\bibitem{HandbookProcessAlgebra}
J.A. Bergstra, A. Ponse, S.A. Smolka, 
\emph{Handbook of Process Algebra}, 
Elsevier Science B.V., 2001

\bibitem{Keller}
R.M. Keller,
\emph{Formal Verification of Parallel Programs},
Communications of the ACM, 19(7), pp. 371-384, 1976

\bibitem{ReactiveSystems}
L. Aceto, A. Ingolfsdottir, K. G. Larsen, J. Srba,
\emph{Reactive Systems - Modeling, Specification and Verification},
Cambridge University Press, 2007

\bibitem{Park}
D.M.R. Park,
\emph{Concurrency and Automata on Infinite Sequences},
In: Proceedings of the 5th G.I.Conference in Theoretical Computer Science, 
Lecture Notes in Computer Science, vol. 104, Springer-Verlag, pp. 167-183, 1981

\bibitem{UnderstandingConcurrentSystems}
A.W. Roscoe,
\emph{Understanding Concurrent Systems},
Texts in Computer Science, Springer-Verlag, 2010

\bibitem{Milner3}
R. Milner,
\emph{Operational and Algebraic Semantics of Concurrency Processes},
In: J. van Leeuwen (ed.) Handbook of Theoretical Computer Science, pp. 1201-1242,
Elsevier and MIT Press, 1990

\bibitem{ModelChecking}
C. Baier, J.-P. Katoen, 
\emph{Principles of Model Checking},
The MIT Press, 2008

\bibitem{Aldebaran}
J.C. Fernandez, 
\emph{Aldebaran: User's Manual},
Technical Report, LGI-IMAG Grenoble, 1988

\bibitem{CWB}
F. Moller, Perdita Stevens,
\emph{{E}dinburgh {C}oncurrency {W}orkbench User Manual (Version 7.1)},	1999,
Available from \url{http://homepages.inf.ed.ac.uk/perdita/cwb/}

\bibitem{mCRL2}
M. van Weerdenburg et al.,
\emph{mCRL2 User's Manual},	2008,
Available from \url{http://www.mcrl2.org}

\bibitem{ProcessAlgebraParallel}
M.Alexander, W.Gardner,
\emph{Process Algebra for Parallel and Distributed Processing},
Chapman\&Hall/CRC Press, Computational Science Series, 2009

\bibitem{Fernandez}
J.C. Fernandez, 
\emph{An Implementation of an Efficient Algorithm for Bisimulation
Equivalence}, Science of Computer Programming, vol. 13, pages 219-236, 1989/1990

\bibitem{ABP1}
W.C. Lynch, 
\emph{Computer systems: Reliable Full-duplex File Transmission over Half-duplex Telephone Line},
Communications of the ACM, vol. 11, no. 6, pp. 407410, 1968

\bibitem{ABP2}
K.A. Bartlett, R.A. Scantlebury, P.T. Wilkinson, 
\emph{A note on Reliable Full-duplex Transmission over Half-duplex Links},
Communications of the ACM, vol. 12, pp. 260261, 1969

%\bibitem{Peterson}
%G.L. Peterson,
%\emph{Myths about the Mutual Exclusion Problem}, 
%Information Processing Letters, 12(3), pages 115-116, 1981

\bibitem{ModellingAndAnalysis}
J.F. Groote, M. Reniers, 
\emph{Modelling and Analysis of Communicating Systems}\emph, 
Technical University of Eindhoven, rev. 1478, 2009

\bibitem{WeakBisimulation}
M.P. Fiore, G.L. Cattani, G. Winskel,
\emph{Weak Bisimulation and Open Map},
BRICS Report Series, 1999

\bibitem{Chomsky}
N. Chomsky,
\emph{Three Models for the Description of Language},
IEEE Transactions on Information Theory, 1956

\bibitem{Compilers}
A.V. Aho, R. Sethi, J.D. Ullman,
\emph{Compilers: Principles, Techniques, and Tools}
Addison Wesley, 2006

\bibitem{ANTLR}
T. Parr, 
\emph{The Definitive ANTLR Reference - Building Domain-Specific Languages}, 
The Pragmatic Bookshelf, 2007

\bibitem{Tarsky}
A. Tarski,
\emph{A Lattice-theoretical Fixpoint Theorem and its Applications},
Pacific Journal of Mathematics 5:2, pp. 285309, 1955

\bibitem{KanellakisSmolka}
P. Kanellakis, S.A. Smolka,
\emph{CCS expressions, finite state processes and three problems of equivalence},
In Proceedings of the 2nd ACM Symposium on Principles of Distributed Computing, pp. 228-240, ACM Press, 1983

\bibitem{PaigeTarjan}
R. Paige, R. Tarjan, 
\emph{Three Partition Refinement Algorithms}\emph, 
SIAM J. Comput. 16 (6), 1987

\bibitem{Kulick}
Seth Kulick,
\emph{Process Algebra, CCS, and Bisimulation Decidability},
University of Pennsylvania, pages 8-10, 1994

%\bibitem{HMLRecursion}
%L. Aceto, A. Ingolfsdottir,
%\emph{Testing Henessy-Milner logic with Recursion},
%BRICS Report Series, pages 3-5, 1998
%
%\bibitem{Dekker}
%E. W. Dijkstra,
%\emph{Co-operating Sequential Processes}, 
%In F. Genuys, editor, Programming Languages, pages 43112. Academic Press, New York, 1968;
%Reprinted from: Technical Report EWD-123, Technological University, Eindhoven, the Netherlands, 1965
%
%\bibitem{PiazzaPolicriti}
%A. Dovier, C. Piazza, A. Policriti, 
%\emph{An Efficient Algorithm for Computing Bisimulation Equivalence}\emph, 
%Theoretical Computer Science 311, pages 221-256, 2004

\end{thebibliography}